Missing data: Current practice in football research and recommendations for reporting missingness

### 2020-09-03 paper/paper.Rmd
add note on missing in Xs and Ys

Imputing data might feel wrong, as we are 'making up data'. The truth
is, we (generally) can never know what the missing values were. The goal
of imputing data is to make the best possible inference from the data.
We recommend data is imputed, with a few caveats. Consider removing
variables with a high proportion of missing data (e.g., variables with
the majority or more missing than not). With respect to a 'rule of
thumb' for when data should be imputed, we deliberately do not suggest
any specific threshold (e.g., impute values when >5% of data are
missing otherwise delete rows with <5% missing) and caution against
such practice. Rather, we recommend values should generally be imputed..
We recommend avoiding imputation methods that impute the same value,
such as mean or median imputation, and instead suggest using imputation
methods such as: linear regression, k nearest neighbours, or expectation
maximisation.

@@

The current state of reporting missing data in the sports literature is
poor. In this section we discuss recommended practices for exploring and
reporting missing data. Our intention is not to provide a 'cookbook'
style approach to missing data, but rather broad recommendations to help
researchers when writing the methods and results sections of a study,
and assist researchers when evaluating a study during the peer-review
process.

>>>>

Imputing data might feel wrong, as we are 'making up data'. The truth
is, we (generally) can never know what the missing values were. The goal
of imputing data is to make the best possible inference from the data.
We recommend data is imputed, with a few caveats. Consider removing
variables with a high proportion of missing data (e.g., variables with
the majority or more missing than not). With respect to a 'rule of
thumb' for when data should be imputed, we deliberately do not suggest
any specific threshold (e.g., impute values when >5% of data are
missing otherwise delete rows with <5% missing) and caution against
such practice. Rather, we recommend values should generally be imputed.

Missing values can occur in the both the predictors (the "independent variables") and response variable (the "dependent variables"). Care should be taken when imputing data, as typically only predictors should be imputed. For discussion on imputing the response value, see ... [@refs]. (note: take a look again)

We recommend avoiding imputation methods that impute the same value,
such as mean or median imputation, and instead suggest using imputation
methods such as: linear regression, k nearest neighbours, or expectation
maximisation.

@@

The current state of reporting missing data in the sports literature has room for improvement. In this section we discuss recommended practices for exploring and
reporting missing data. Our intention is not to provide a 'cookbook'
style approach to missing data, but rather broad recommendations to help
researchers when writing the methods and results sections of a study,
and assist researchers when evaluating a study during the peer-review
process.
